\documentclass[a4paper]{article}

\usepackage[top=0pt, bottom=0pt, left=0pt, right=0pt]{geometry}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{fontspec}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{ragged2e}
\usepackage[absolute,overlay]{textpos}

\definecolor{sidebar}{RGB}{0, 102, 102}
\definecolor{sidetext}{RGB}{255, 255, 255}
\definecolor{sidedesc}{RGB}{224, 224, 224}
\definecolor{siderule}{RGB}{255, 255, 255}
\definecolor{maintext}{RGB}{62, 62, 62}
\definecolor{accent}{RGB}{26, 176, 179}
\definecolor{iconcolor}{RGB}{185, 185, 185}
\definecolor{mainrule}{RGB}{180, 180, 180}

\setmainfont{Inter}[
  Path=fonts/inter/extras/ttf/,
  Extension=.ttf,
  UprightFont=Inter-Regular,
  BoldFont=Inter-Bold,
]

\newfontfamily\rubik{Rubik-Variable}[
  Path=fonts/rubik/,
  Extension=.ttf,
]

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\setlength{\TPHorizModule}{1pt}
\setlength{\TPVertModule}{1pt}

\newcommand{\sidebarsection}[1]{%
  \vspace{17pt}%
  {\rubik\fontsize{10.1}{12}\selectfont\color{sidetext}\MakeUppercase{#1}\par}%
  \vspace{3pt}%
  {\fontsize{1}{1}\selectfont\color{siderule!40}\rule{\linewidth}{0.4pt}\par}%
  \vspace{6pt}%
}

\newcommand{\mainsection}[1]{%
  \vspace{17pt}%
  {\rubik\fontsize{10.1}{12}\selectfont\color{maintext}\MakeUppercase{#1}\par}%
  \vspace{3pt}%
  {\fontsize{1}{1}\selectfont\color{mainrule}\rule{\linewidth}{0.4pt}\par}%
  \vspace{6pt}%
}

\newcommand{\experienceheader}[2]{%
  {\rubik\fontsize{9.5}{11.5}\selectfont\color{maintext}#1\hfill}%
  {\fontsize{7.6}{9.5}\selectfont\color{maintext}#2\par}%
}

\newcommand{\experiencecompanyonly}[1]{%
  {\rubik\fontsize{8.9}{10.5}\selectfont\color{accent}#1\par}%
  \vspace{2pt}%
}

\newcommand{\experiencecompanyloc}[2]{%
  {\rubik\fontsize{8.9}{10.5}\selectfont\color{accent}#1\hfill}%
  {\fontsize{7.6}{9.5}\selectfont\color{maintext}#2\par}%
  \vspace{2pt}%
}

\newcommand{\experiencebullet}[1]{%
  \hangindent=11pt\hangafter=1%
  {\fontsize{7.6}{9.5}\selectfont\color{maintext}\textbullet\hspace{4pt}#1\par}%
}

\newcommand{\sideaward}[1]{%
  \hangindent=17pt\hangafter=1%
  {\color{sidetext}\faIcon{trophy}}\hspace{6pt}%
  {\rubik\fontsize{9.5}{11.5}\selectfont\color{sidetext}#1\par}%
  \vspace{12pt}%
}

\newcommand{\sideachievement}[2]{%
  \hangindent=17pt\hangafter=1%
  {\color{sidetext}\faIcon{trophy}}\hspace{6pt}%
  {\rubik\fontsize{9.5}{11.5}\selectfont\color{sidetext}#1\par}%
  \vspace{2pt}%
  {\fontsize{7.6}{9.5}\selectfont\color{sidedesc}#2\par}%
  \vspace{8pt}%
}

\newcommand{\proficiencydots}[1]{%
  \foreach \i in {1,...,5}{%
    \ifnum\i>#1\relax%
      \tikz[baseline=-0.5ex]\draw[sidetext, line width=0.5pt] (0,0) circle (2pt);%
    \else%
      \tikz[baseline=-0.5ex]\fill[sidetext] (0,0) circle (2pt);%
    \fi%
    \hspace{0.5pt}%
  }%
}

\begin{document}

% Draw sidebar background
\begin{tikzpicture}[remember picture, overlay]
  \fill[sidebar] (current page.north west) rectangle ([xshift=207pt]current page.south west);
\end{tikzpicture}

% ============= SIDEBAR CONTENT =============
\begin{textblock*}{153pt}(31pt, 31pt)
\parskip=0pt\relax%
\color{sidetext}%
{\rubik\fontsize{17.8}{21}\selectfont MOHANKUMAR\\RAMACHANDRAN\par}%

\vspace{18pt}%

\sidebarsection{Key Achievements}

\sideachievement{Open-Source AI Native IDE}{Gained 2K+ GitHub stars and 15K+ downloads, with zero marketing}

\sideachievement{Interactive Portfolio Website}{A Windows XP-themed web experience that tells my childhood story}

\sideachievement{Built 3D Scanner}{End-to-end photogrammetry scanner, built from scratch in 3 months}

\sideachievement{Innovative QR File Transfer}{Developed a tool enabling 100\% offline file transfers using QR codes}

\sidebarsection{Publications}

{\rubik\fontsize{9.5}{11.5}\selectfont\color{sidetext}Method and System for\\Facilitating Payment\\Transactions in Offline Mode\par}%
\vspace{5pt}%
{\fontsize{7.6}{9.5}\selectfont\color{sidedesc}\href{https://www.tdcommons.org/dpubs_series/3754/}{https://www.tdcommons.org/dpubs\_series\\/3754/}\par}%
\vspace{10pt}%
{\rubik\fontsize{9.5}{11.5}\selectfont\color{sidetext}Method and System for\\Processing Queries with Query\\Filters on a Server\par}%
\vspace{5pt}%
{\fontsize{7.6}{9.5}\selectfont\color{sidedesc}\href{https://www.tdcommons.org/dpubs_series/5562/}{https://www.tdcommons.org/dpubs\_series\\/5562/}\par}%

\sidebarsection{Skills}

{\fontsize{7.6}{12}\selectfont\color{sidetext}%
Agentic AI \textperiodcentered{} LangGraph \textperiodcentered{} LangChain\par
RAG Pipelines \textperiodcentered{} Langfuse \textperiodcentered{} Python\par
TypeScript \textperiodcentered{} JavaScript \textperiodcentered{} FastAPI\par
Nuxt \textperiodcentered{} Vue.js \textperiodcentered{} Tailwind CSS\par
Cloudflare Workers \textperiodcentered{} AWS \textperiodcentered{} Hadoop\par}%

\sidebarsection{Open Source}

{\fontsize{7.6}{9.5}\selectfont\color{sidedesc}Merged PRs to:\par}%
\vspace{4pt}%
{\fontsize{7.6}{10}\selectfont\color{sidetext}%
\textbullet\hspace{4pt}Microsoft VS Code\par
\textbullet\hspace{4pt}LangChain-AI / LangGraph\par
\textbullet\hspace{4pt}Hono.js\par
\textbullet\hspace{4pt}Continue (AI IDE)\par
\textbullet\hspace{4pt}Google Firebase\par
\textbullet\hspace{4pt}A2A Protocol\par
\textbullet\hspace{4pt}Portkey AI Gateway\par
\textbullet\hspace{4pt}and many more\par}%

\sidebarsection{Languages}

\vspace{1pt}%
{\rubik\fontsize{8.9}{12}\selectfont\color{sidetext}Tamil}%
\hfill%
\proficiencydots{5}%
\hspace{3pt}%
{\fontsize{7.6}{12}\selectfont\color{sidetext}Native\par}%
\vspace{6pt}%
{\rubik\fontsize{8.9}{12}\selectfont\color{sidetext}English}%
\hfill%
\proficiencydots{4}%
\hspace{3pt}%
{\fontsize{7.6}{12}\selectfont\color{sidetext}Proficient\par}%

\end{textblock*}

% ============= MAIN CONTENT =============
\begin{textblock*}{342pt}(223pt, 27pt)
\parskip=0pt\relax%
\color{maintext}%

\hspace{7pt}{\fontsize{10.1}{12}\selectfont\color{accent}Open Source Contributor \textbar{} Tech Blogger \textbar{} Software Engineer\par}%
\vspace{8pt}%

\hspace{7pt}{\fontsize{8.2}{13}\selectfont\color{maintext}%
\mbox{{\color{iconcolor}\faGithub}\hspace{4pt}{\rubik \href{https://github.com/mohankumarelec}{https://github.com/mohankumarelec}}}%
\hspace{10pt}%
\mbox{{\color{iconcolor}\faGlobe}\hspace{4pt}{\rubik \href{https://mohanram.dev}{https://mohanram.dev}}}\par}%
\hspace{7pt}{\fontsize{8.2}{13}\selectfont\color{maintext}%
\mbox{{\color{iconcolor}\faEnvelope}\hspace{4pt}{\rubik \href{mailto:mail@mohanram.dev}{mail@mohanram.dev}}}%
\hspace{14pt}%
\mbox{{\color{iconcolor}\faLinkedin}\hspace{4pt}{\rubik \href{https://www.linkedin.com/in/mohrama}{https://www.linkedin.com/in/mohrama}}}\par}%

\mainsection{Summary}

{\fontsize{7.6}{9.5}\selectfont\color{maintext}%
Engineer at heart — I like building things that work well and sharing them with the world. Over the years, I've worked across AI, data, full-stack, and infrastructure, picking up whatever's needed to ship good software.\par}%
\vspace{8pt}%
{\fontsize{7.6}{9.5}\selectfont\color{maintext}%
Most of my side projects end up open source. I learn best by building, and if it helps someone else along the way, even better.\par}%
\vspace{8pt}%
{\fontsize{7.6}{9.5}\selectfont\color{maintext}%
When I'm not coding for work, I'm usually tinkering with my homelab — self-hosting things, breaking things, fixing things.\par}%

\mainsection{Experience}

\experienceheader{Principal Software Engineer}{01/2026 - Present}
\experiencecompanyonly{\href{https://www.redhat.com}{Red Hat}}

\experiencebullet{Building agentic AI systems at scale — end-to-end development covering observability, evaluation, scalability, and production-grade deployment pipelines.}

\vspace{12pt}
\experienceheader{Full Stack Generative AI Engineer}{04/2025 - 01/2026}
\experiencecompanyonly{\href{https://www.gsk.com}{GSK Plc}}

\experiencebullet{Built AIGA, a LangGraph-inspired Python framework for GenAI app development with reusable agents and sub-agents, enabling rapid prototyping and deployment across GSK.}

\experiencebullet{Designed standardized protocol wrappers (A2A, MCP) to expose agents and tools for cross-team and cross-platform AI integration across GSK.}

\vspace{12pt}
\experienceheader{Founder}{08/2024 - 04/2025}
\experiencecompanyonly{\href{https://flexpilot.ai}{Flexpilot AI}}

\experiencebullet{Founded flexpilot.ai, an open-source AI-native IDE and VS Code extension — hit \textbf{2K+ GitHub stars} and \textbf{15K+ marketplace downloads} with zero marketing or promotion.}

\experiencebullet{Only open-source IDE to support GitHub Copilot Extensions (Agent Marketplace) while using VS Code's native UI.}

\vspace{12pt}
\experienceheader{Data Scientist / Data Engineer}{06/2019 - 08/2024}
\experiencecompanyloc{\href{https://corporate.visa.com}{Visa Inc.}}{Bengaluru, India}

\experiencebullet{Built an OpenAI-compatible proxy server for Visa's internal AI platform, letting developers use frameworks like LangChain directly — increased developer productivity by 2x and won the company hackathon.}

\experiencebullet{Built generative AI tools for the sales team to create presentations using Office JavaScript APIs.}

\experiencebullet{Led a next-gen analytics platform for analyzing billion-dollar revenue data using Hadoop, Hive, Spark, and Tableau.}

\experiencebullet{Built a custom semantic layer with a JDBC driver to optimize BI query routing, reducing license costs by \$5M annually and winning a separate company hackathon.}

\vspace{12pt}
\experienceheader{Freelancer}{08/2015 - 06/2019}
\experiencecompanyloc{\href{https://www.freelancer.in/u/mohankumarelec}{https://www.freelancer.in/u/mohankumarelec}}{Chennai, India}

\experiencebullet{Designed and delivered solutions in Python, Node.js, and Gen AI with a 95\%+ client satisfaction rate across multiple freelance projects.}

\mainsection{Education}

\experienceheader{M.Tech, Electrical Engineering}{06/2018 - 06/2019}
\experiencecompanyonly{\href{https://www.iitm.ac.in}{Indian Institute of Technology Madras}}

\vspace{2pt}
\experienceheader{B.Tech, Electrical Engineering}{06/2014 - 06/2018}
\experiencecompanyonly{\href{https://www.iitm.ac.in}{Indian Institute of Technology Madras}}

\mainsection{Fun Projects}

\experienceheader{Air-Gapped QR Code Transfer}{11/2023 - 12/2023}
\vspace{4pt}

{\fontsize{7.6}{9.5}\selectfont\color{maintext}%
Web-based tool for 100\% offline file transfer via QR codes — built with Vue.js, pako, qrcode.js, and zbar-wasm for encoding, compression, and scanning.\par}%
\vspace{3pt}%
{\fontsize{7.6}{9.5}\selectfont\color{maintext}%
\href{https://github.com/mohankumarelec/airgapped-qr-code-transfer}{https://github.com/mohankumarelec/airgapped-qr-code-transfer}\par}%

\end{textblock*}

\mbox{}

\end{document}